An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-09-30 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edit

In this paper we present the `cmpsR` package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets in Hamby study [@hamby] to show its potential for further research.
The CMPS algorithm was proposed by NIST in 2019 and was made for objective tool marks comparisons.
We introduce the basic logic of the CMPS algorithm and lay out its implementation in the `cmpsR` package.
We also showcase the functionality of the `cmpsR` package with a small dataset example that is included in the package.
In the `cmpsR` package we implement some graphing tools for users to visualize results and to gain a better understanding of both the algorithm and the results.

>>>>

In this paper we present the `cmpsR` package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets from the Hamby study [@hamby] to show its potential for further research.
The CMPS algorithm was proposed by NIST in 2019 and was made for objective tool marks comparisons.
We introduce the basic logic of the CMPS algorithm and lay out its implementation in the `cmpsR` package.
We also showcase the functionality of the `cmpsR` package with a small dataset example that is included in the package.
In the `cmpsR` package we implement some graphing tools for users to visualize results and to gain a better understanding of both the algorithm and the results.
